GSE158422: DNA methylation in Lung squamous cell carcinoma - gene methylation enrichment analysis

### 2023-10-03 figs/GSE158422_split.Rmd
progress

CORES=28

@@

aal <- function(mval,myann,genesets,design,cores=1) {
  medf <- chragg(mval,myann,cores=CORES)
  agag <- gsagg(x=medf,genesets=gs_symbols,cores=CORES)
  aal <- aalimma(agag=agag,design=design)
  return(aal)
}

aalres <- aal(mval=mval,myann=myann,genesets=gs_symbols,design=design,cores=CORES)

@@

  # la1
  dm1 <- runlimma(mval_a,design_a,myann)
  dmagg1 <- agg(dm1,cores=CORES)
  m1 <- dmagg1$gme_res_df[,"mean",drop=FALSE]
  lares1 <- ttenrich(m=m1,genesets=gs_symbols,cores=CORES)

  # la2
  dm2 <- runlimma(mval_b,design_b,myann)
  dmagg2 <- agg(dm2,cores=CORES)
  m2 <- dmagg2$gme_res_df[,"mean",drop=FALSE]
  lares2 <- ttenrich(m=m2,genesets=gs_symbols,cores=CORES)

@@

lares <- lapply( seq(100,5000,100) ,splitanalyze_la)

@@

  #al
  medf1 <- chragg(mval_a,myann,cores=CORES)
  magg1 <- agglimma(medf1,design_a)
  m1 <- as.data.frame(magg1$t)
  rownames(m1) <- rownames(magg1)
  colnames(m1) <- "t"
  alres1 <- ttenrich(m=m1,genesets=gs_symbols,cores=CORES)

  #al
  medf2 <- chragg(mval_b,myann,cores=CORES)
  magg2 <- agglimma(medf2,design_b)
  m2 <- as.data.frame(magg2$t)
  rownames(m2) <- rownames(magg2)
  colnames(m2) <- "t"
  alres2 <- ttenrich(m=m2,genesets=gs_symbols,cores=CORES)

@@

alres <- lapply( seq(100,5000,100) ,splitanalyze_al)

@@

  #aa1
  aares1 <- aal(mval=mval_a,myann=myann,genesets=gs_symbols,
    design=design_a,cores=CORES)

  #aa2
  aares2 <- aal(mval=mval_b,myann=myann,genesets=gs_symbols,
    design=design_b,cores=CORES)

@@

aares <- lapply( seq(100,5000,100) ,splitanalyze_aa)

@@

aacompare <-function(aares){
  aares1 <- aares[[1]]
  aares2 <- aares[[2]]
  aasig1 <- subset(aares1,adj.P.Val<0.05)
  aasig2 <- subset(aares2,adj.P.Val<0.05)

@@

barplot(res$common,main="no. common",names.arg=c("la","al","aa"))
barplot(res$uncommon,main="no. uncommon",names.arg=c("la","al","aa"))
barplot(res$discordant,main="no. discordant",names.arg=c("la","al","aa"))

boxplot(list("la"=laout$common,"al"=alout$common,"aa"=aaout$common),
  main="no. common",col="white",ylim=c(0,1550))
beeswarm(list("la"=laout$common,"al"=alout$common,"aa"=aaout$common), add=TRUE,cex=1.2,pch=19)

boxplot(list("la"=laout$uncommon,"al"=alout$uncommon,"aa"=aaout$uncommon),
  main="no. uncommon",col="white",ylim=c(0,1550))
beeswarm(list("la"=laout$uncommon,"al"=alout$uncommon,"aa"=aaout$uncommon), add=TRUE,cex=1.2,pch=19)

boxplot(list("la"=laout$discordant,"al"=alout$discordant,"aa"=aaout$discordant),
  main="no. discordant",col="white",ylim=c(0,1550))
beeswarm(list("la"=laout$discordant,"al"=alout$discordant,"aa"=aaout$discordant), add=TRUE,cex=1.2,pch=19)

barplot(res$p_comm,main="proportion common",names.arg=c("la","al","aa"))
barplot(res$p_uncom,main="proportion uncommon",names.arg=c("la","al","aa"))
barplot(res$p_disc,main="proportion discordant",names.arg=c("la","al","aa"))

boxplot(list("la"=laout$p_comm,"al"=alout$p_comm,"aa"=aaout$p_comm),
  main="proportion common",col="white",ylim=c(0,1))
beeswarm(list("la"=laout$p_comm,"al"=alout$p_comm,"aa"=aaout$p_comm), add=TRUE,cex=1.2,pch=19)

boxplot(list("la"=laout$p_uncom,"al"=alout$p_uncom,"aa"=aaout$p_uncom),
  main="proportion uncommon",col="white",ylim=c(0,1))
beeswarm(list("la"=laout$p_uncom,"al"=alout$p_uncom,"aa"=aaout$p_uncom), add=TRUE,cex=1.2,pch=19)

boxplot(list("la"=laout$p_disc,"al"=alout$p_disc,"aa"=aaout$p_disc),
  main="proportion discordant",col="white",ylim=c(0,1))
beeswarm(list("la"=laout$p_disc,"al"=alout$p_disc,"aa"=aaout$p_disc), add=TRUE,cex=1.2,pch=19)

>>>>

CORES=8

@@

aal <- function(mval,myann,genesets,design,cores=1) {
  medf <- chragg(mval,myann,cores=CORES)
  agag <- gsagg(x=medf,genesets=gs_symbols,cores=CORES)
  aalres <- aalimma(agag=agag,design=design)
  return(aalres)
}

#aalres <- aal(mval=mval,myann=myann,genesets=gs_symbols,design=design,cores=CORES)

@@

  # la1
  dm1 <- runlimma(mval_a,design_a,myann)
  dmagg1 <- agg(dm1,cores=floor(CORES/3))
  m1 <- dmagg1$gme_res_df[,"mean",drop=FALSE]
  lares1 <- ttenrich(m=m1,genesets=gs_symbols,cores=CORES)

  # la2
  dm2 <- runlimma(mval_b,design_b,myann)
  dmagg2 <- agg(dm2,cores=floor(CORES/3))
  m2 <- dmagg2$gme_res_df[,"mean",drop=FALSE]
  lares2 <- ttenrich(m=m2,genesets=gs_symbols,cores=CORES)

@@

lares <- mclapply( seq(100,5000,100) ,splitanalyze_la,mc.cores=CORES)

@@

  #al
  medf1 <- chragg(mval_a,myann,cores=floor(CORES/3))
  magg1 <- agglimma(medf1,design_a)
  m1 <- as.data.frame(magg1$t)
  rownames(m1) <- rownames(magg1)
  colnames(m1) <- "t"
  alres1 <- ttenrich(m=m1,genesets=gs_symbols,cores=CORES)

  #al
  medf2 <- chragg(mval_b,myann,cores=floor(CORES/3))
  magg2 <- agglimma(medf2,design_b)
  m2 <- as.data.frame(magg2$t)
  rownames(m2) <- rownames(magg2)
  colnames(m2) <- "t"
  alres2 <- ttenrich(m=m2,genesets=gs_symbols,cores=CORES)

@@

alres <- mclapply( seq(100,5000,100) ,splitanalyze_al,mc.cores=CORES)

@@

  #aa1
  aares1 <- aal(mval=mval_a,myann=myann,genesets=gs_symbols,
    design=design_a,cores=floor(CORES/3))

  #aa2
  aares2 <- aal(mval=mval_b,myann=myann,genesets=gs_symbols,
    design=design_b,cores=floor(CORES/3))

@@

aares <- mclapply( seq(100,5000,100) ,splitanalyze_aa,mc.cores=CORES)

@@

aacompare <-function(aa){
  aa1 <- aa[[1]]
  aa2 <- aa[[2]]
  aasig1 <- subset(aa1,adj.P.Val<0.05)
  aasig2 <- subset(aa2,adj.P.Val<0.05)

@@

barplot(res$common,main="no. common",names.arg=c("LA","AL","AA"))
barplot(res$uncommon,main="no. uncommon",names.arg=c("LA","AL","AA"))
barplot(res$discordant,main="no. discordant",names.arg=c("LA","AL","AA"))

boxplot(list("LA"=laout$common,"AL"=alout$common,"AA"=aaout$common),
  main="no. common",col="white",ylim=c(0,1550))
beeswarm(list("LA"=laout$common,"AL"=alout$common,"AA"=aaout$common), add=TRUE,cex=1.2,pch=19)

boxplot(list("LA"=laout$uncommon,"AL"=alout$uncommon,"AA"=aaout$uncommon),
  main="no. uncommon",col="white",ylim=c(0,1550))
beeswarm(list("LA"=laout$uncommon,"AL"=alout$uncommon,"AA"=aaout$uncommon), add=TRUE,cex=1.2,pch=19)

boxplot(list("LA"=laout$discordant,"AL"=alout$discordant,"AA"=aaout$discordant),
  main="no. discordant",col="white",ylim=c(0,1550))
beeswarm(list("LA"=laout$discordant,"AL"=alout$discordant,"AA"=aaout$discordant), add=TRUE,cex=1.2,pch=19)

barplot(res$p_comm,main="proportion common",names.arg=c("LA","AL","AA"))
barplot(res$p_uncom,main="proportion uncommon",names.arg=c("LA","AL","AA"))
barplot(res$p_disc,main="proportion discordant",names.arg=c("LA","AL","AA"))

boxplot(list("LA"=laout$p_comm,"AL"=alout$p_comm,"AA"=aaout$p_comm),
  main="proportion common",col="white",ylim=c(0,1))
beeswarm(list("LA"=laout$p_comm,"AL"=alout$p_comm,"AA"=aaout$p_comm), add=TRUE,cex=1.2,pch=19)

boxplot(list("LA"=laout$p_uncom,"AL"=alout$p_uncom,"AA"=aaout$p_uncom),
  main="proportion uncommon",col="white",ylim=c(0,1))
beeswarm(list("LA"=laout$p_uncom,"AL"=alout$p_uncom,"AA"=aaout$p_uncom), add=TRUE,cex=1.2,pch=19)

boxplot(list("LA"=laout$p_disc,"AL"=alout$p_disc,"AA"=aaout$p_disc),
  main="proportion discordant",col="white",ylim=c(0,1))
beeswarm(list("LA"=laout$p_disc,"AL"=alout$p_disc,"AA"=aaout$p_disc), add=TRUE,cex=1.2,pch=19)
